A Gaussian process model of human electrocorticographic data

### 2020-02-13 paper/main.tex
finished revamping freq breakdown section, starting on most informative electrode section

Although both datasets we examined provide good full-brain coverage
(when considering data from every patient; e.g.\
Fig.~\ref{fig:corrmap}C, D), electrodes were not sampled uniformly
throughout the brain.  For example, electrodes are more likely to be
implanted in regions like the medial temporal lobe (MTL), and are
rarely implanted in occipital cortex (Fig.~\ref{fig:density}A, B).
Separately for each dataset, for each voxel in the 4~mm$^3$ voxel
MNI152 brain, we computed the proportion of electrodes in the dataset
that were contained within a 20 MNI unit radius sphere centered on
that voxel.  We defined the \textit{density} at that location as this
proportion.  Across Datasets 1 and 2, the electrode placement
densities were similar (correlation by voxel:
$r = 0.6, p < 10^{-10}$).  We wondered whether regions with good
covererage might be associated with better reconstruction accuracy.
For example, Figures~\ref{fig:corrmap}C and D indicate that many
electrodes in the MTL (which tends to be relatively densely sampled)
have relatively high reconstruction accuracy, and occipital electrodes
(which tends to be relatively sparsely sampled) tend to have
relatively low reconstruction accuracy.  To test whether this held
more generally across the entire brain, for each dataset we computed
the electrode placement density for each electrode from each patient
(using the proportion of \textit{other} patients' electrodes within 20
MNI units of the given electrode).  We then correlated these density
values with the across-patient reconstruction accuracies for each
electrode.  We found a statistically reliable negative correlation
between reconstruction accuracy and density for Dataset 1, but no
reliable correlation for Dataset 2 (Dataset 1: $r = -0.21, p = 0.05$;
Dataset 2: $r = -0.30, p = 0.15$).  This indicates that the
reconstruction accuracies we observed are \textit{not} driven solely
by sampling density, but rather may also reflect higher order
properties of neural dynamics such as functional correlations between
distant voxels~\citep{BetzEtal17b}.

%%%%%%%%%%%%%%%%%%%%% MOVE FREQEUNCY STUFF HERE

@@

@@

We also wondered what frequency properties contributed to the
reconstruction accuracy. To recover frequency-band specific voltage activity
from each recording, a second-order Butterworth filter was applied
across bands $\delta$, $\theta$, $\alpha$, $\beta$, $\gamma_L$, and
$\gamma_H$ with respective frequency ranges 2-4 Hz, 4-8 Hz, 8-12 Hz,
12-30 Hz, 30-60 Hz, and 60-100 Hz. Bandpass signals contain
information about the phase and amplitude of the underlying frequency
band, providing the most detailed view of the activity at that
frequency. Additionally, we calculated the reconstruction accuracies
using power at each band by taking the absolute
value of the Hilbert tranform of the bandpassed signal (see Fig.~\freqpower). To compute the broadband power (BB), we
first computed instantaneous power at 50 log-spaced frequencies
between 2 and 100 Hz using Morlet wavelets (n=4). Then, for each time
point and electrode, we fitted a robust Huber regression to frequency
and power in log-space, and calculated the mean height of the
resulting line. We then followed the same procedure outlined above
(see Fig.~\ref{fig:methods}) to
obtain the reconstruction accuracy at each bandpassed frequency as well
as broadband power for both datasets (see Fig.~\ref{fig:frequency}).
We found
the best average reconstruction accuracy for each dataset was obtained using broadband
power, which is a correlate of neural firing
~\citep{MannEtal09}. We also found a similar trend in reconstruction
accuracy for frequency bands across the two datasets, performing better at lower
frequencies (peaking at $\alpha$) and worst at high frequencies (see Fig.~\ref{fig:frequency}).

>>>>

Although both datasets we examined provide good full-brain coverage
(when considering data from every patient; e.g.\
Fig.~\ref{fig:corrmap}C, D), electrodes were not sampled uniformly
throughout the brain.  For example, electrodes are more likely to be
implanted in regions like the medial temporal lobe (MTL), and are
rarely implanted in occipital cortex (Fig.~\ref{fig:density}A, B).
Separately for each dataset, for each voxel in the 4~mm$^3$ voxel
MNI152 brain, we computed the proportion of electrodes in the dataset
that were contained within a 20 MNI unit radius sphere centered on
that voxel.  We defined the \textit{density} at that location as this
proportion.  Across Datasets 1 and 2, the electrode placement
densities were similar (correlation by voxel:
$r = 0.6, p < 10^{-10}$).  We wondered whether regions with good
covererage might be associated with better reconstruction accuracy.
For example, Figures~\ref{fig:corrmap}C and D indicate that many
electrodes in the MTL (which tends to be relatively densely sampled)
have relatively high reconstruction accuracy, and occipital electrodes
(which tends to be relatively sparsely sampled) tend to have
relatively low reconstruction accuracy.  To test whether this held
more generally across the entire brain, for each dataset we computed
the electrode placement density for each electrode from each patient
(using the proportion of \textit{other} patients' electrodes within 20
MNI units of the given electrode).  We then correlated these density
values with the across-patient reconstruction accuracies for eachg
electrode.  We found a statistically reliable negative correlation
between reconstruction accuracy and density for Dataset 1, but no
reliable correlation for Dataset 2 (Dataset 1: $r = -0.21, p = 0.05$;
Dataset 2: $r = -0.30, p = 0.15$).  This indicates that the
reconstruction accuracies we observed are \textit{not} driven solely
by sampling density, but rather may also reflect higher order
properties of neural dynamics such as functional correlations between
distant voxels~\citep{BetzEtal17b}.

Prior work in humans and animals has shown that the spatial profile of
the local field potential differs by frequency band~\citep[e.g., with
respect to volume conductance properties and contribution to the local
field potential;][]{BuzsEtal12, FrieEtal07, CronEtal11}.  For example,
lower frequency components of the local field potential tend to have
higher power and extend further in space than high-frequency
components~\citep[e.g., ][]{MillEtal07, MannEtal09}.  We therefore
wondered whether the reconstructions we observed might be differently
weighting or considering the contributions of activity at different
frequency bands.  We therefore examined a range of frequency bands
($\delta$: 2--4 Hz; $\theta$: 4--8 Hz; $\alpha$: 8--12 Hz; $\beta$:
12--30 Hz; $\gamma_L$: 30--60 Hz; and $\gamma_H$: 60--100 Hz), along
with a measure of broadband power~\citep[defined as the mean height of
a linear robust regression fit in log-log space to the order 4 Morelet
wavelet-computed power spectrum at 50 log-spaced frequencies from from
2--100 Hz;][]{MannEtal09}.  We used second-order Butterworth bandpass
filters to compute the activity patterns within each narrow frequency
band.  We then repeated our within-subject and across-subject
cross-validated reconstruction accuracy tests (analogous to
Fig.~\ref{fig:corrmaps}) separately for each frequency band
(Fig.~\ref{fig:frequency}).  (We also carried out a similar analysis
on the Hilbert transform-computed spectral power within each narrow
band; see Fig.~\freqpower.)  Across both datasets, we found that our
approach is best at reconstructing patterns of broadband activity
(right-most bars in Figs.~\ref{fig:frequency}A and D), a correlate of
population firing rate~\citep{MannEtal09}.  We also achieved good
reconstruction accuracy within each narrow frequency band
(Figs.~\ref{fig:frequency} and \freqpower).  Activity at lower
frequencies ($\delta$, $\theta$, $\alpha$, and $\beta$) tended to be
reconstructed better than high-frequency patterns ($\gamma_L$ and
$\gamma_H$), with reconstruction accuracy peaking in the $\alpha$
band.  Overall, these results indicate that our approach is able to
accurately recover information within the 2--100 Hz range, although
those reconstructions are most accurate for low-frequency or broadband patterns.

@@

%%%%%%%%% STOPPED HERE

@@
